% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  11pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
  \setmainfont[]{DejaVu Serif}
  \setmonofont[Scale=0.82]{DejaVu Sans Mono}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[top=2.5cm,bottom=2.5cm,left=2.8cm,right=2.8cm]{geometry}
\usepackage{listings}
\newcommand{\passthrough}[1]{#1}
\lstset{defaultdialect=[5.3]Lua}
\lstset{defaultdialect=[x86masm]Assembler}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{SpeakPrep: System Design and Architecture}
\author{Abhiyan Sainju}
\date{April 2026}

\begin{document}
\maketitle

\hypertarget{speakprep-document-2-system-design-architecture}{%
\section{SpeakPrep --- Document 2: System Design +
Architecture}\label{speakprep-document-2-system-design-architecture}}

\hypertarget{version-1.0-author-abhiyan-sainju-april-2026}{%
\subsubsection{Version 1.0 \textbar{} Author: Abhiyan Sainju \textbar{}
April 2026}\label{version-1.0-author-abhiyan-sainju-april-2026}}

\hypertarget{cross-references-doc-1-prd-doc-3-build-guide-doc-4-interview-story}{%
\subsubsection{Cross-references: Doc 1 (PRD), Doc 3 (Build Guide), Doc 4
(Interview
Story)}\label{cross-references-doc-1-prd-doc-3-build-guide-doc-4-interview-story}}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\begin{quote}
\textbf{How to use this doc:} This is your technical bible. It explains
WHAT the system does and HOW each component works --- both at the
architecture level and at the concept level. When you're confused about
why something is built a certain way, the answer should be here. Read it
once before building, reference it constantly during.
\end{quote}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{table-of-contents}{%
\subsection{TABLE OF CONTENTS}\label{table-of-contents}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \protect\hyperlink{1-system-overview}{System Overview}
\item
  \protect\hyperlink{2-real-time-audio-deep-concepts}{Real-Time Audio:
  Deep Concepts}
\item
  \protect\hyperlink{3-voice-activity-detection}{Voice Activity
  Detection}
\item
  \protect\hyperlink{4-websocket-architecture}{WebSocket Architecture}
\item
  \protect\hyperlink{5-python-asyncio--asgi-deep-concepts}{Python
  Asyncio + ASGI: Deep Concepts}
\item
  \protect\hyperlink{6-asr-how-whisper-and-deepgram-work}{ASR: How
  Whisper and Deepgram Work}
\item
  \protect\hyperlink{7-llm-integration--streaming}{LLM Integration +
  Streaming}
\item
  \protect\hyperlink{8-tts-how-kokoro-works}{TTS: How Kokoro Works}
\item
  \protect\hyperlink{9-full-pipeline-data-flow}{Full Pipeline Data Flow}
\item
  \protect\hyperlink{10-database-design}{Database Design}
\item
  \protect\hyperlink{11-caching-layer-valkey}{Caching Layer: Valkey}
\item
  \protect\hyperlink{12-authentication--security}{Authentication +
  Security}
\item
  \protect\hyperlink{13-infrastructure-architecture}{Infrastructure
  Architecture}
\item
  \protect\hyperlink{14-observability--monitoring}{Observability +
  Monitoring}
\item
  \protect\hyperlink{15-architecture-decision-records-adrs}{Architecture
  Decision Records (ADRs)}
\end{enumerate}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{system-overview}{%
\subsection{1. System Overview}\label{system-overview}}

\hypertarget{what-the-system-must-do}{%
\subsubsection{What the system must do}\label{what-the-system-must-do}}

SpeakPrep's core loop, from the system's perspective:

\begin{lstlisting}
1. Maintain a persistent WebSocket connection per active session
2. Receive audio binary chunks from the browser
3. Detect when the user finishes speaking (VAD)
4. Transcribe the audio to text (ASR)
5. Generate an intelligent response from the LLM
6. Convert that response to audio (TTS)
7. Stream the audio back to the browser
8. Log everything: latency, transcripts, scores
9. Persist conversation state across reconnects
\end{lstlisting}

Every component in the system exists to serve one of these nine
functions.

\hypertarget{high-level-architecture-diagram}{%
\subsubsection{High-Level Architecture
Diagram}\label{high-level-architecture-diagram}}

\begin{lstlisting}
┌───────────────────────────────────────────────────────────────────┐
│                         BROWSER (Chrome/Firefox)                  │
│                                                                   │
│  [React Web App]                                                  │
│  ┌────────────────────────────────────────────────────────────┐   │
│  │  Microphone API → MediaRecorder → Opus/WebM chunks         │   │
│  │  AudioContext → Decode PCM → Play audio chunks             │   │
│  │  WebSocket client → send audio, receive audio + text       │   │
│  └────────────────────────────────────────────────────────────┘   │
└────────────────────────┬──────────────────────────────────────────┘
                         │ WSS (WebSocket Secure)
                         │ Cloudflare Tunnel (encrypted)
                         ↓
┌───────────────────────────────────────────────────────────────────┐
│                  ORACLE CLOUD ARM VM (24 GB RAM)                  │
│                                                                   │
│  ┌──────────────────────────────────────────────────────────┐     │
│  │                    CADDY (reverse proxy)                  │     │
│  │  Routes /api/* → FastAPI                                  │     │
│  │  Routes /ws/* → FastAPI WebSocket                         │     │
│  │  Automatic HTTPS via Let's Encrypt                        │     │
│  └──────────────────────────────────────────────────────────┘     │
│                              ↓                                    │
│  ┌──────────────────────────────────────────────────────────┐     │
│  │              FASTAPI APPLICATION (Python 3.12)            │     │
│  │  ┌─────────────┐ ┌─────────────┐ ┌─────────────────────┐ │     │
│  │  │  REST API   │ │  WebSocket  │ │  Background Tasks   │ │     │
│  │  │  Auth/Users │ │  Handler    │ │  Scoring, Reports   │ │     │
│  │  │  Sessions   │ │  per session│ │  (asyncio tasks)    │ │     │
│  │  └─────────────┘ └──────┬──────┘ └─────────────────────┘ │     │
│  └─────────────────────────│────────────────────────────────┘     │
│                             │ Internal HTTP                       │
│          ┌──────────────────┼──────────────────┐                  │
│          ↓                  ↓                  ↓                  │
│  ┌─────────────┐   ┌─────────────┐    ┌─────────────┐            │
│  │ FASTER-     │   │  KOKORO     │    │   VALKEY    │            │
│  │ WHISPER     │   │  TTS API    │    │  (Redis)    │            │
│  │ (ASR)       │   │  (port 8880)│    │  Session    │            │
│  │ (port 9000) │   └─────────────┘    │  Cache      │            │
│  └─────────────┘                      └─────────────┘            │
│                                                                   │
│                    EXTERNAL API CALLS                             │
│  ┌──────────────────────────────────────────────────────────┐     │
│  │  Groq API (LLM) → api.groq.com                           │     │
│  │  Deepgram API (streaming ASR) → api.deepgram.com         │     │
│  │  Supabase (PostgreSQL + Auth) → [project].supabase.co    │     │
│  └──────────────────────────────────────────────────────────┘     │
└───────────────────────────────────────────────────────────────────┘

                    EXTERNAL SERVICES
┌─────────────────────────────────────────────────────────────────┐
│  Cloudflare — DNS, CDN, DDoS, Tunnel                            │
│  New Relic — APM, metrics, dashboards                           │
│  Sentry — Error tracking                                        │
│  PostHog — Product analytics + LLM observability               │
│  GitHub Actions — CI/CD pipeline                               │
└─────────────────────────────────────────────────────────────────┘
\end{lstlisting}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{real-time-audio-deep-concepts}{%
\subsection{2. Real-Time Audio: Deep
Concepts}\label{real-time-audio-deep-concepts}}

\hypertarget{why-audio-is-hard-and-what-you-need-to-know}{%
\subsubsection{Why Audio is Hard (and What You Need to
Know)}\label{why-audio-is-hard-and-what-you-need-to-know}}

Before you write a single line of audio code, you need to understand
what you're actually manipulating. Audio feels like a black box until
you understand the bytes.

\hypertarget{sample-rate-what-it-means}{%
\subsubsection{Sample Rate: What It
Means}\label{sample-rate-what-it-means}}

\textbf{Sample rate} is how many times per second we measure the air
pressure (amplitude of the sound wave). A sample rate of \textbf{16,000
Hz (16 kHz)} means we take 16,000 measurements per second.

\textbf{Why 16 kHz for voice ASR?} - Human speech intelligibility lives
in the \textbf{100 Hz -- 8 kHz frequency range} - Nyquist's theorem: to
capture frequencies up to 8 kHz accurately, you need at least 16,000
samples/second - Higher sample rates (44.1 kHz, 48 kHz) add zero ASR
accuracy --- Whisper, Deepgram, and every major ASR model internally
downsamples to 16 kHz anyway - At 44.1 kHz you'd be sending 2.75x more
data for identical results

\textbf{What a sample actually is:} Each sample is a signed 16-bit
integer --- a number between -32,768 and +32,767. Positive numbers
represent compression waves (louder), negative numbers represent
rarefaction waves. Zero = silence. Maximum amplitude (clipping) =
±32,767.

\hypertarget{pcm-the-raw-format}{%
\subsubsection{PCM: The Raw Format}\label{pcm-the-raw-format}}

\textbf{PCM (Pulse-Code Modulation)} is audio in its rawest form ---
just a sequence of these 16-bit integers, one per sample, in time order.
No compression, no headers (mostly), just the numbers.

For our pipeline: \textbf{16,000 samples/second × 2 bytes/sample × 1
channel (mono) = 32,000 bytes/second = 32 KB/s.}

This is the format Whisper expects internally. Everything else (MP3,
Opus, WebM) is PCM plus compression.

\hypertarget{audio-frames-and-chunking}{%
\subsubsection{Audio Frames and
Chunking}\label{audio-frames-and-chunking}}

We don't process audio as one continuous stream --- we process it in
\textbf{frames} (fixed-size chunks). Why?

\begin{itemize}
\tightlist
\item
  VAD needs to analyze audio in segments to detect speech vs silence
\item
  Streaming requires sending data incrementally, not waiting for the
  full recording
\item
  Processing latency must stay bounded --- you can't wait for 30 seconds
  of audio before starting
\end{itemize}

\textbf{Frame size decisions:}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Frame Size
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Samples (16kHz)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Bytes
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Latency Added
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Tradeoff
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
10ms & 160 & 320 & 10ms & Low latency, high overhead (100 frames/sec) \\
20ms & 320 & 640 & 20ms & ✅ Best balance --- used by WebRTC VAD \\
30ms & 480 & 960 & 30ms & Slightly lower overhead \\
100ms & 1,600 & 3,200 & 100ms & Too much latency for real-time \\
\end{longtable}

\textbf{Our choice: 20ms frames (640 bytes each).} This is the standard
for voice AI pipelines.

\hypertarget{audio-in-the-browser}{%
\subsubsection{Audio in the Browser}\label{audio-in-the-browser}}

The browser's \textbf{MediaRecorder API} captures microphone audio, but
it doesn't give you raw PCM. It gives you encoded audio (WebM/Opus on
Chrome, OGG/Opus on Firefox). You have two options:

\textbf{Option A (simpler, less control): Use MediaRecorder}

\begin{lstlisting}
const mediaRecorder = new MediaRecorder(stream, {
  mimeType: 'audio/webm;codecs=opus',
  audioBitsPerSecond: 16000
});
mediaRecorder.ondataavailable = (event) => {
  websocket.send(event.data); // Send Opus/WebM chunks
};
mediaRecorder.start(20); // Get data every 20ms
\end{lstlisting}

\textbf{Problem:} You get Opus-encoded chunks --- you must decode
server-side before feeding to Whisper.

\textbf{Option B (complex, full control): Use Web Audio API}

\begin{lstlisting}
const audioContext = new AudioContext({ sampleRate: 16000 });
const source = audioContext.createMediaStreamSource(stream);
const processor = audioContext.createScriptProcessor(320, 1, 1); // 20ms at 16kHz
processor.onaudioprocess = (event) => {
  const pcmData = event.inputBuffer.getChannelData(0); // Float32Array
  const int16Data = float32ToInt16(pcmData); // Convert to PCM Int16
  websocket.send(int16Data.buffer); // Send raw PCM
};
source.connect(processor);
processor.connect(audioContext.destination);
\end{lstlisting}

\textbf{Advantage:} Server receives raw PCM --- no decoding needed,
direct to VAD and Whisper.

\textbf{Our recommendation for SpeakPrep:} Use Option B (Web Audio API
with ScriptProcessor) for Phase 1. It's more code but eliminates
server-side decoding overhead and gives you direct control for VAD.

\begin{quote}
\textbf{📚 Learn more:} MDN Web Audio API docs, ``Audio and Video in
HTML5'' chapter from O'Reilly
\end{quote}

\hypertarget{bandwidth-reality-check}{%
\subsubsection{Bandwidth Reality Check}\label{bandwidth-reality-check}}

\begin{lstlisting}
Raw PCM:   32,000 bytes/sec = 32 KB/s = 256 kbps per user
Opus 32kbps: 4,000 bytes/sec = 4 KB/s = 32 kbps per user (8:1 compression)

At 50 concurrent users:
- Raw PCM: 50 × 32 KB/s = 1.6 MB/s upload to server
- Opus: 50 × 4 KB/s = 200 KB/s upload to server

Oracle's free egress bandwidth: ~10 TB/month
At 50 users × 2 hrs/day: 200 KB/s × 3,600s × 365 = ~262 GB/year. Well within limits.
\end{lstlisting}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{voice-activity-detection}{%
\subsection{3. Voice Activity
Detection}\label{voice-activity-detection}}

\hypertarget{the-problem-vad-solves}{%
\subsubsection{The Problem VAD Solves}\label{the-problem-vad-solves}}

If you send audio to Whisper without VAD: 1. Whisper processes silence
and \textbf{hallucinates} --- it generates random text on quiet audio
(this affects 40.3\% of non-speech segments) 2. You transcribe the
user's coughs, breathing, and background noise 3. You can't detect when
the user stops talking to trigger transcription

VAD is the gatekeeper: only real speech passes through.

\hypertarget{how-webrtc-vad-works-conceptually}{%
\subsubsection{How WebRTC VAD Works
(Conceptually)}\label{how-webrtc-vad-works-conceptually}}

WebRTC VAD is a \textbf{Gaussian Mixture Model (GMM)} classifier. Here's
what that means:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Feature extraction:} For each 20ms audio frame, compute a set
  of spectral features using FFT --- essentially ``what frequencies are
  dominant in this chunk of audio?''
\item
  \textbf{GMM classification:} Compare those features against learned
  probability distributions of ``what speech looks like'' vs ``what
  noise/silence looks like.'' A GMM is just a statistical model
  representing these distributions as overlapping Gaussian curves.
\item
  \textbf{Binary decision:} Output speech=1 or silence=0 based on which
  distribution is more likely.
\end{enumerate}

\textbf{Aggressiveness modes (0--3):} - Mode 0: Very permissive ---
catches all speech, including whispers. More false positives (noise
classified as speech) - Mode 3: Very strict --- only confident speech
passes. May clip soft speech or sentence endings

\textbf{Code for WebRTC VAD:}

\begin{lstlisting}[language=Python]
import webrtcvad
import collections

vad = webrtcvad.Vad(mode=2)  # Aggressiveness 0-3

def is_speech(audio_frame: bytes, sample_rate: int = 16000) -> bool:
    """
    audio_frame must be 10, 20, or 30ms of audio
    At 16kHz with 16-bit mono: 20ms = 640 bytes
    """
    return vad.is_speech(audio_frame, sample_rate)

def collect_speech_segment(audio_queue, silence_threshold_ms=500):
    """
    Collect audio frames until we detect sustained silence.
    silence_threshold_ms: how long silence must persist before we stop recording
    """
    speech_frames = []
    silence_frames = collections.deque(maxlen=silence_threshold_ms // 20)
    triggered = False
    
    for frame in audio_queue:
        is_speech_frame = is_speech(frame)
        
        if not triggered:
            if is_speech_frame:
                triggered = True
                speech_frames.append(frame)
        else:
            speech_frames.append(frame)
            if not is_speech_frame:
                silence_frames.append(frame)
                # Check if we have enough consecutive silence
                if len(silence_frames) == silence_frames.maxlen:
                    if all(not is_speech(f) for f in silence_frames):
                        break  # End of utterance
            else:
                silence_frames.clear()  # Reset silence counter
    
    return b''.join(speech_frames)
\end{lstlisting}

\hypertarget{silero-vad-better-for-production}{%
\subsubsection{Silero VAD: Better for
Production}\label{silero-vad-better-for-production}}

Silero VAD uses a small LSTM neural network trained on massive
multilingual data. It outputs a \textbf{confidence score (0.0--1.0)}
rather than binary. This enables: - \textbf{Adaptive thresholding:}
Start speaking at 0.5 confidence, stop at 0.35 (hysteresis prevents
flickering) - \textbf{Noisy environment robustness:} Handles background
TV, street noise, HVAC - \textbf{Multi-language support:} Works without
language-specific tuning

\textbf{Integration:}

\begin{lstlisting}[language=Python]
import torch
model, utils = torch.hub.load(repo_or_dir='snakers4/silero-vad', model='silero_vad')
(get_speech_timestamps, _, read_audio, *_) = utils

def silero_detect_speech(audio_tensor):
    """
    audio_tensor: torch.Tensor of Float32 audio at 16kHz
    Returns: list of {start, end} timestamps where speech occurs
    """
    return get_speech_timestamps(audio_tensor, model, sampling_rate=16000)
\end{lstlisting}

\hypertarget{end-of-utterance-detection-the-latency-budget}{%
\subsubsection{End-of-Utterance Detection: The Latency
Budget}\label{end-of-utterance-detection-the-latency-budget}}

The 500ms silence threshold is the industry default --- but it adds
500ms to every turn. If you target 2 seconds total latency, you can't
afford to waste 500ms just waiting.

\textbf{Solutions (in order of complexity):}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Aggressive VAD (350ms):} Reduce silence threshold. Risk: clips
  sentence endings like ``\ldots and that's why I think\ldots{} that
  approach works.'' Try 350ms first.
\item
  \textbf{Punctuation streaming:} If using Deepgram streaming, they
  detect end-of-utterance semantically and return
  \passthrough{\lstinline!is\_final: true!} --- often before silence
  completes.
\item
  \textbf{Semantic endpointing:} Use a small fast model that reads
  partial transcript and predicts ``is this sentence complete?'' Can
  fire 200--300ms before silence ends. This is how LiveKit's EOU model
  achieves sub-200ms detection.
\end{enumerate}

\textbf{For SpeakPrep Phase 1:} Use 400ms silence threshold with WebRTC
VAD mode 2. Target 350ms in Phase 2 after measuring actual impact.

\begin{quote}
\textbf{📚 Learn more:} Silero VAD GitHub (snakers4/silero-vad), WebRTC
VAD paper, LiveKit blog on semantic endpointing
\end{quote}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{websocket-architecture}{%
\subsection{4. WebSocket Architecture}\label{websocket-architecture}}

\hypertarget{protocol-level-understanding}{%
\subsubsection{Protocol-Level
Understanding}\label{protocol-level-understanding}}

WebSocket begins as an HTTP request with special headers:

\begin{lstlisting}
Client → Server:
GET /ws/voice/session-123 HTTP/1.1
Host: api.speakprep.com
Upgrade: websocket
Connection: Upgrade
Sec-WebSocket-Key: dGhlIHNhbXBsZSBub25jZQ==
Sec-WebSocket-Version: 13

Server → Client:
HTTP/1.1 101 Switching Protocols
Upgrade: websocket
Connection: Upgrade
Sec-WebSocket-Accept: s3pPLMBiTxaQ9kYGzzhZRbK+xOo=
\end{lstlisting}

After this handshake, the connection is \textbf{upgraded} --- it's no
longer HTTP. It's a raw TCP connection with WebSocket framing.

\textbf{Frame structure:}

\begin{lstlisting}
Byte 0: FIN bit (1 = final fragment) + RSV1/2/3 (extensions) + Opcode
         Opcodes: 0x1=text, 0x2=binary, 0x8=close, 0x9=ping, 0xA=pong
Byte 1: MASK bit + Payload length (7 bits, or 16/64 bit extended)
Bytes 2-5: Masking key (client→server only — client MUST mask)
Remaining: Payload (XOR'd with masking key if masked)
\end{lstlisting}

\textbf{Why do clients have to mask frames?} Prevents cache poisoning
attacks --- if an intermediary proxy sees a WebSocket frame without
masking, it might mistake it for an HTTP response and cache it,
poisoning the cache for other users.

\hypertarget{speakprep-websocket-message-protocol}{%
\subsubsection{SpeakPrep WebSocket Message
Protocol}\label{speakprep-websocket-message-protocol}}

Define a clear message schema before building. This prevents protocol
drift as the app evolves.

\textbf{Client → Server messages:}

\begin{lstlisting}[language=Python]
# All messages are JSON, except type="audio_chunk" which is binary

# 1. Authentication (first message after connect, must arrive within 5 seconds)
{
  "type": "auth",
  "token": "eyJhbGciOiJIUzI1NiJ9..."
}

# 2. Session start
{
  "type": "session_start",
  "session_id": "550e8400-e29b-41d4-a716",
  "interview_type": "behavioral",  # or "technical", "system_design", "mixed"
  "difficulty": "intermediate",
  "persona": "challenging",
  "duration_minutes": 30
}

# 3. Audio data (BINARY frame, not JSON)
# Raw binary: Float32 PCM samples or Opus-encoded WebM
# Header convention: first 4 bytes = sequence number (uint32)

# 4. Audio end signal (user released push-to-talk, or VAD confirmed end)
{
  "type": "audio_end",
  "sequence": 42,
  "duration_ms": 4200
}

# 5. Barge-in (user started speaking while AI was talking)
{
  "type": "barge_in"
}

# 6. Heartbeat
{
  "type": "ping",
  "timestamp": 1714500000000
}
\end{lstlisting}

\textbf{Server → Client messages:}

\begin{lstlisting}[language=Python]
# 1. Auth result
{"type": "auth_result", "success": true, "user_id": "uuid"}

# 2. Session ready
{"type": "session_ready", "first_question": "Let's start..."}

# 3. Transcription (real-time, may update as ASR processes)
{
  "type": "transcript",
  "text": "I led the migration of our monolith to microservices...",
  "is_final": false,  # true = final transcript for this turn
  "confidence": 0.92
}

# 4. AI response text (streamed token by token)
{
  "type": "llm_token",
  "token": "That",
  "sequence": 0
}

# 5. TTS audio chunk (BINARY frame)
# First 4 bytes: sequence number (uint32, big-endian)
# Remaining: Opus audio data
# Client plays chunks in sequence order, buffering if needed

# 6. Turn complete (AI finished responding)
{
  "type": "turn_complete",
  "turn_id": "uuid",
  "latencies": {
    "asr_ms": 412,
    "llm_ttft_ms": 287,
    "tts_first_ms": 309,
    "total_ms": 1248
  },
  "live_scores": {
    "filler_words": 3,
    "speaking_rate_wpm": 148,
    "estimated_star_compliance": 0.75
  }
}

# 7. Error
{
  "type": "error",
  "code": "ASR_FAILED",
  "message": "Speech recognition failed — please try again",
  "recoverable": true
}

# 8. Session end
{
  "type": "session_end",
  "session_id": "uuid",
  "summary": {...}
}

# 9. Heartbeat response
{"type": "pong", "timestamp": 1714500000000}
\end{lstlisting}

\hypertarget{websocket-handler-in-fastapi}{%
\subsubsection{WebSocket Handler in
FastAPI}\label{websocket-handler-in-fastapi}}

\begin{lstlisting}[language=Python]
from fastapi import WebSocket, WebSocketDisconnect
from typing import Dict
import asyncio
import json
import uuid

class ConnectionManager:
    """Manages all active WebSocket connections."""
    
    def __init__(self):
        # Maps session_id → WebSocket
        self.active_connections: Dict[str, WebSocket] = {}
    
    async def connect(self, websocket: WebSocket, session_id: str):
        await websocket.accept()
        self.active_connections[session_id] = websocket
    
    async def disconnect(self, session_id: str):
        self.active_connections.pop(session_id, None)
    
    async def send_json(self, session_id: str, data: dict):
        ws = self.active_connections.get(session_id)
        if ws:
            await ws.send_json(data)
    
    async def send_bytes(self, session_id: str, data: bytes):
        ws = self.active_connections.get(session_id)
        if ws:
            await ws.send_bytes(data)

manager = ConnectionManager()

@app.websocket("/ws/voice/{session_id}")
async def voice_endpoint(websocket: WebSocket, session_id: str):
    await manager.connect(websocket, session_id)
    
    try:
        # Step 1: Authentication (must arrive in 5 seconds)
        auth_msg = await asyncio.wait_for(
            websocket.receive_json(), 
            timeout=5.0
        )
        if not await authenticate(auth_msg.get("token")):
            await websocket.close(code=4001, reason="Unauthorized")
            return
        
        # Step 2: Initialize session
        session = await Session.create(session_id)
        audio_buffer = bytearray()
        
        # Step 3: Main message loop
        async for message in websocket.iter_bytes():
            if isinstance(message, bytes):
                # Binary = audio data
                audio_buffer.extend(message)
                
                # Run VAD on latest 20ms frame
                frame = bytes(audio_buffer[-640:])
                if vad.is_speech(frame, 16000):
                    pass  # Continue collecting
                else:
                    if len(audio_buffer) > 3200:  # At least 100ms of audio
                        # End of utterance detected
                        audio_data = bytes(audio_buffer)
                        audio_buffer.clear()
                        
                        # Process in background, continue receiving
                        asyncio.create_task(
                            process_turn(websocket, session, audio_data)
                        )
    
    except WebSocketDisconnect:
        await manager.disconnect(session_id)
        await cleanup_session(session_id)
    except asyncio.TimeoutError:
        await websocket.close(code=4002, reason="Auth timeout")
\end{lstlisting}

\hypertarget{heartbeat-reconnection}{%
\subsubsection{Heartbeat + Reconnection}\label{heartbeat-reconnection}}

\begin{lstlisting}[language=Python]
# Server-side heartbeat — detect dead connections
async def heartbeat_monitor(websocket: WebSocket, session_id: str):
    while True:
        await asyncio.sleep(20)  # Ping every 20 seconds
        try:
            pong = await asyncio.wait_for(
                websocket.receive_json(), 
                timeout=5.0
            )
            # Connection is alive
        except asyncio.TimeoutError:
            # Connection is dead — clean up
            await manager.disconnect(session_id)
            break
\end{lstlisting}

\begin{lstlisting}
// Client-side reconnection with exponential backoff
class VoiceConnection {
    constructor(sessionId) {
        this.sessionId = sessionId;
        this.ws = null;
        this.reconnectAttempts = 0;
        this.maxAttempts = 10;
    }
    
    async connect() {
        return new Promise((resolve, reject) => {
            this.ws = new WebSocket(`wss://api.speakprep.com/ws/voice/${this.sessionId}`);
            
            this.ws.onopen = () => {
                // Send auth immediately
                this.ws.send(JSON.stringify({
                    type: "auth",
                    token: localStorage.getItem('access_token')
                }));
                this.reconnectAttempts = 0;
                resolve();
            };
            
            this.ws.onclose = (event) => {
                if (event.code !== 1000) { // 1000 = normal close
                    this.scheduleReconnect();
                }
            };
        });
    }
    
    scheduleReconnect() {
        if (this.reconnectAttempts >= this.maxAttempts) return;
        
        // Exponential backoff: 500ms, 1s, 2s, 4s, 8s, ... capped at 30s
        const delay = Math.min(500 * Math.pow(2, this.reconnectAttempts), 30000);
        // Add jitter: ±25% to prevent thundering herd
        const jitter = delay * 0.25 * (Math.random() * 2 - 1);
        
        setTimeout(() => {
            this.reconnectAttempts++;
            this.connect();
        }, delay + jitter);
    }
}
\end{lstlisting}

\begin{quote}
\textbf{📚 Learn more:} RFC 6455 (WebSocket Protocol), FastAPI WebSocket
docs, MDN WebSocket API
\end{quote}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{python-asyncio-asgi-deep-concepts}{%
\subsection{5. Python Asyncio + ASGI: Deep
Concepts}\label{python-asyncio-asgi-deep-concepts}}

\hypertarget{the-event-loop-what-it-actually-is}{%
\subsubsection{The Event Loop: What It Actually
Is}\label{the-event-loop-what-it-actually-is}}

Python's asyncio event loop is a \textbf{scheduler}. Not a thread pool.
Not a process pool. A single-threaded scheduler that decides which
coroutine to run next.

Here's what happens when you have 3 concurrent voice sessions:

\begin{lstlisting}
Time 0ms: Event loop starts
Time 1ms: Session A connects, starts waiting for audio
Time 2ms: Session B connects, starts waiting for audio  
Time 3ms: Session C connects, starts waiting for audio

[All three are now "suspended" — they're waiting for I/O. The event loop is idle.]

Time 100ms: Session A sends audio data
→ Event loop wakes session A's coroutine
→ Session A sends audio to Deepgram API
→ Session A hits `await` while waiting for Deepgram response
→ Event loop suspends session A, picks up session B/C if they have work

Time 150ms: Deepgram responds to Session A
→ Event loop wakes session A again
→ Session A sends transcript to Groq
→ Session A hits `await` again (waiting for Groq)
→ Event loop can advance sessions B and C while A waits
\end{lstlisting}

This is \textbf{cooperative multitasking} --- coroutines voluntarily
yield at \passthrough{\lstinline!await!} points. The event loop can't
interrupt a coroutine mid-execution (that's preemptive multitasking). If
you accidentally write blocking code (like calling
\passthrough{\lstinline!requests.get()!} synchronously), you block the
entire event loop.

\hypertarget{what-asyncawait-actually-means}{%
\subsubsection{\texorpdfstring{What \texttt{async/await} Actually
Means}{What async/await Actually Means}}\label{what-asyncawait-actually-means}}

\begin{lstlisting}[language=Python]
# This is a COROUTINE FUNCTION (notice the async)
async def process_audio(audio_data: bytes) -> str:
    # This line suspends THIS coroutine and yields control to the event loop
    # The event loop can run other coroutines while we wait for Deepgram
    transcript = await deepgram_client.transcribe(audio_data)
    
    # When Deepgram responds, the event loop resumes HERE
    return transcript

# A coroutine function returns a COROUTINE OBJECT when called
# It doesn't execute until you await it or create a Task
coro = process_audio(data)  # Nothing happens yet

# Option 1: await directly (sequential)
result = await process_audio(data)

# Option 2: Create a Task (concurrent — runs in background)
task = asyncio.create_task(process_audio(data))
# Do other things...
result = await task  # Wait for it when you need the result
\end{lstlisting}

\hypertarget{the-gil-and-why-it-doesnt-matter-here}{%
\subsubsection{The GIL and Why It Doesn't Matter
Here}\label{the-gil-and-why-it-doesnt-matter-here}}

The \textbf{Global Interpreter Lock (GIL)} prevents two Python threads
from executing Python bytecode simultaneously. Many developers think
this makes Python bad for concurrent applications.

\textbf{For voice AI, the GIL is irrelevant.} Here's why:

All the expensive work in our pipeline is I/O-bound or runs outside
Python: - \textbf{Waiting for Deepgram API response:} OS-level I/O, GIL
released - \textbf{Waiting for Groq API response:} OS-level I/O, GIL
released - \textbf{Faster-Whisper inference:} CTranslate2 is C++ with
GIL released during inference - \textbf{Kokoro TTS inference:} PyTorch
releases GIL during tensor operations

The GIL \emph{would} matter if we were doing CPU-bound Python
computation (like matrix multiplication in pure Python). We're not.

\hypertarget{asgi-what-it-is}{%
\subsubsection{ASGI: What It Is}\label{asgi-what-it-is}}

\textbf{WSGI} (Flask/Django's standard) is a synchronous protocol: the
server calls your app with a request, your app returns a response.
Period. No way to push data to clients or maintain persistent
connections.

\textbf{ASGI} adds: - Async/await support (coroutines instead of
threads) - WebSocket handling (bidirectional persistent connections) -
HTTP/2 and HTTP/3 push - Background tasks

\begin{lstlisting}[language=Python]
# ASGI application interface (conceptual)
async def application(scope, receive, send):
    """
    scope: dict with connection info (type, headers, path, etc.)
    receive: async callable to receive messages from client
    send: async callable to send messages to client
    """
    if scope['type'] == 'websocket':
        # Handle WebSocket
        event = await receive()  # e.g., {'type': 'websocket.connect'}
        if event['type'] == 'websocket.connect':
            await send({'type': 'websocket.accept'})
        
        while True:
            event = await receive()
            if event['type'] == 'websocket.receive':
                # Process message
                await send({
                    'type': 'websocket.send',
                    'text': 'response'
                })
\end{lstlisting}

FastAPI implements this for you --- you write the handler, FastAPI
handles the ASGI scaffold.

\hypertarget{how-many-concurrent-connections-can-we-handle}{%
\subsubsection{How Many Concurrent Connections Can We
Handle?}\label{how-many-concurrent-connections-can-we-handle}}

\begin{lstlisting}
Single Uvicorn process with uvloop:
- Each WebSocket = ~1 asyncio.Task
- Each Task = ~8 KB stack frame
- 1 GB RAM for connections = ~131,000 connections (theoretical)
- Real-world with voice AI processing: ~500–1,000 active sessions
  (limited by external API rate limits, not connection count)

With 4 Gunicorn workers on Oracle ARM (4 OCPUs):
- 4 × 1,000 = ~4,000 concurrent sessions
- Requires Redis for cross-worker session state sharing
- Well beyond Phase 1 needs (target: 50 concurrent)
\end{lstlisting}

\begin{quote}
\textbf{📚 Learn more:} ``Python Concurrency with asyncio'' by Matthew
Fowler (Manning), Real Python asyncio guide, PEP 3156 (asyncio
specification), PEP 3333 (WSGI), PEP 3492 (ASGI)
\end{quote}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{asr-how-whisper-and-deepgram-work}{%
\subsection{6. ASR: How Whisper and Deepgram
Work}\label{asr-how-whisper-and-deepgram-work}}

\hypertarget{whispers-architecture-what-the-model-actually-does}{%
\subsubsection{Whisper's Architecture (What the Model Actually
Does)}\label{whispers-architecture-what-the-model-actually-does}}

Whisper is a \textbf{Transformer encoder-decoder model} trained on
680,000 hours of audio-transcript pairs collected from the web.

\textbf{Step 1: Audio preprocessing} Raw 16kHz audio → 30-second window
(zero-padded) → \textbf{log-mel spectrogram} with 80 frequency bins.

What is a mel spectrogram? It's a visual representation of audio that
matches human hearing perception. The ``mel'' scale compresses high
frequencies (we can't distinguish 8000 Hz from 8100 Hz well) and expands
low frequencies (we can clearly distinguish 100 Hz from 200 Hz). The log
transform compresses the amplitude range.

\begin{lstlisting}[language=Python]
# Conceptually, what Whisper's preprocessing does:
import numpy as np
import librosa

audio = load_audio("input.wav", sr=16000)  # Raw PCM

# Compute mel spectrogram
mel = librosa.feature.melspectrogram(
    y=audio, sr=16000, n_mels=80,
    n_fft=400,     # 25ms window
    hop_length=160  # 10ms hop
)
log_mel = librosa.power_to_db(mel)  # Log scale
\end{lstlisting}

\textbf{Step 2: Encoder} The mel spectrogram passes through 2 Conv1D
layers (for local feature extraction) then through N transformer blocks
(12 for small, 24 for large). Each transformer block has: - Multi-head
self-attention (tokens attend to other tokens) - Feed-forward network
(pointwise transformation) - Layer normalization

Output: contextualized audio representations (``what acoustic patterns
are here?'')

\textbf{Step 3: Decoder} Autoregressively generates text tokens. At each
step: 1. Takes previously generated tokens as input 2. Applies causal
self-attention (can only see previous tokens, not future ones) 3.
Applies cross-attention to encoder output (this is how text ``attends''
to audio) 4. Outputs probability distribution over vocabulary 5. Sample
the most likely token (temperature affects this) 6. Repeat until
\passthrough{\lstinline!<|endoftext|>!} token

\textbf{Why Whisper has a 30-second limit:} The model was trained on
30-second windows. Longer audio requires chunking and merging, which
introduces errors at boundaries.

\hypertarget{faster-whisper-and-ctranslate2}{%
\subsubsection{Faster-Whisper and
CTranslate2}\label{faster-whisper-and-ctranslate2}}

Original Whisper runs PyTorch with float32 weights. CTranslate2 applies:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{INT8 quantization:} Convert weights from 32-bit floats to
  8-bit integers. This reduces model size 4x and improves inference
  speed 2--4x with \textless1\% accuracy loss on most languages.
\item
  \textbf{Layer fusion:} Combine operations that can run together (e.g.,
  matrix multiply + bias add + activation) into single CUDA/CPU kernels.
\item
  \textbf{Batched inference:} Process multiple audio files
  simultaneously --- better GPU utilization.
\item
  \textbf{Optimal memory layout:} Weights stored in memory layout that
  matches CPU cache patterns.
\end{enumerate}

\textbf{Performance comparison:}

\begin{lstlisting}
Whisper small (PyTorch, float32, CPU): ~18 seconds for 60-second audio
faster-whisper small (CTranslate2, INT8, CPU): ~4.5 seconds (4x faster)
faster-whisper small (CTranslate2, INT8, GPU): ~0.9 seconds (20x faster)
\end{lstlisting}

\hypertarget{deepgram-how-streaming-asr-works-differently}{%
\subsubsection{Deepgram: How Streaming ASR Works
Differently}\label{deepgram-how-streaming-asr-works-differently}}

Deepgram's Nova-3 is a \textbf{CTC (Connectionist Temporal
Classification)} model, not an encoder-decoder. CTC allows: - Processing
audio frames as they arrive (no 30-second window constraint) -
Outputting partial results continuously - Sub-300ms latency from speech
to transcript

\textbf{Streaming integration with Deepgram:}

\begin{lstlisting}[language=Python]
from deepgram import DeepgramClient, LiveTranscriptionEvents, LiveOptions

async def stream_to_deepgram(audio_queue, result_callback):
    dg = DeepgramClient(api_key=DEEPGRAM_API_KEY)
    
    options = LiveOptions(
        model="nova-3",
        language="en",
        encoding="linear16",  # Raw PCM
        sample_rate=16000,
        channels=1,
        interim_results=True,   # Get partial results
        endpointing=380,        # 380ms silence = end of utterance
        smart_format=True,      # Add punctuation
        utterance_end_ms="1000" # Alternative endpointing
    )
    
    connection = dg.listen.asynclive.v("1")
    
    @connection.on(LiveTranscriptionEvents.Transcript)
    async def on_transcript(result, **kwargs):
        transcript = result.channel.alternatives[0].transcript
        if result.is_final:
            await result_callback(transcript)
    
    await connection.start(options)
    
    async for audio_chunk in audio_queue:
        await connection.send(audio_chunk)
    
    await connection.finish()
\end{lstlisting}

\hypertarget{asr-hallucination-prevention}{%
\subsubsection{ASR Hallucination
Prevention}\label{asr-hallucination-prevention}}

\textbf{What hallucination looks like:}

\begin{lstlisting}
[10 seconds of silence]
Whisper output: "Thank you for watching. Please like and subscribe."

[User clears throat]  
Whisper output: "The weather today is sunny with a high of 72 degrees."
\end{lstlisting}

\textbf{Multi-layer prevention:}

\begin{lstlisting}[language=Python]
async def transcribe_with_validation(audio: bytes) -> Optional[str]:
    # Layer 1: VAD check — don't transcribe if Silero says <0.5 confidence
    if not await silero_vad_check(audio):
        return None
    
    # Layer 2: Transcribe
    segments, info = whisper_model.transcribe(audio, language="en")
    transcript = " ".join([s.text for s in segments])
    
    # Layer 3: Check no-speech probability (Whisper outputs this)
    if info.no_speech_prob > 0.6:
        return None
    
    # Layer 4: Compression ratio (hallucinations are usually repetitive)
    import zlib
    compressed = zlib.compress(transcript.encode())
    compression_ratio = len(transcript.encode()) / len(compressed)
    if compression_ratio > 2.4:  # Very repetitive = likely hallucination
        return None
    
    # Layer 5: Minimum length (transcribing 5+ seconds with <3 words = suspect)
    words = transcript.strip().split()
    audio_duration = len(audio) / (16000 * 2)  # seconds
    if audio_duration > 3 and len(words) < 2:
        return None
    
    return transcript.strip()
\end{lstlisting}

\begin{quote}
\textbf{📚 Learn more:} Whisper paper (arxiv.org/abs/2212.04356),
CTranslate2 GitHub, Deepgram streaming docs, ``Robust Speech Recognition
via Large-Scale Weak Supervision''
\end{quote}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{llm-integration-streaming}{%
\subsection{7. LLM Integration +
Streaming}\label{llm-integration-streaming}}

\hypertarget{token-streaming-how-it-works}{%
\subsubsection{Token Streaming: How It
Works}\label{token-streaming-how-it-works}}

LLM APIs return tokens as they're generated --- you don't wait for the
complete response. This is critical for voice AI because it lets TTS
start synthesizing while the LLM is still generating.

\textbf{The Groq streaming API (OpenAI-compatible):}

\begin{lstlisting}[language=Python]
from groq import AsyncGroq

client = AsyncGroq(api_key=GROQ_API_KEY)

async def stream_llm_response(messages: list) -> AsyncIterator[str]:
    stream = await client.chat.completions.create(
        model="llama-3.3-70b-versatile",
        messages=messages,
        stream=True,
        temperature=0.7,
        max_tokens=300  # Keep responses short for voice
    )
    
    async for chunk in stream:
        delta = chunk.choices[0].delta
        if delta.content:
            yield delta.content  # Yield one token at a time
\end{lstlisting}

\hypertarget{sentence-level-tts-buffering}{%
\subsubsection{Sentence-Level TTS
Buffering}\label{sentence-level-tts-buffering}}

The key insight: TTS needs complete sentences (or at least complete
phrases), not individual tokens. You accumulate tokens until you have a
complete sentence, then synthesize it while continuing to collect the
next sentence.

\begin{lstlisting}[language=Python]
import re

SENTENCE_ENDINGS = re.compile(r'(?<=[.!?;:])\s+|(?<=\n)\n')
ABBREVIATIONS = {'Dr', 'Mr', 'Mrs', 'Ms', 'Prof', 'Sr', 'Jr', 
                 'vs', 'etc', 'Inc', 'Corp', 'Ltd', 'Co',
                 'e.g', 'i.e', 'a.k.a'}

def is_sentence_boundary(text: str, pos: int) -> bool:
    """Check if position pos is a real sentence boundary."""
    if pos >= len(text):
        return False
    
    # Check if the period is part of an abbreviation
    before = text[:pos].split()[-1] if text[:pos].split() else ""
    if before.rstrip('.') in ABBREVIATIONS:
        return False
    
    # Check if it's a decimal number like "3.14"
    if pos > 0 and text[pos-1].isdigit() and pos < len(text) and text[pos].isdigit():
        return False
    
    return True

async def tts_streaming_pipeline(
    llm_stream: AsyncIterator[str],
    websocket: WebSocket,
    kokoro_client
):
    """
    Triple-buffer pipeline:
    - Collect LLM tokens into sentence buffer
    - When sentence complete, synthesize immediately
    - Send TTS audio chunks to client as they're generated
    """
    sentence_buffer = ""
    tts_tasks = []
    
    async for token in llm_stream:
        sentence_buffer += token
        
        # Check for sentence boundary
        # Look for ". " or "? " or "! " patterns
        for match in SENTENCE_ENDINGS.finditer(sentence_buffer):
            if is_sentence_boundary(sentence_buffer, match.start()):
                sentence = sentence_buffer[:match.start() + 1].strip()
                sentence_buffer = sentence_buffer[match.end():]
                
                if sentence:
                    # Fire-and-forget TTS synthesis
                    task = asyncio.create_task(
                        synthesize_and_send(sentence, websocket, kokoro_client)
                    )
                    tts_tasks.append(task)
    
    # Handle remaining buffer (last sentence without terminal punctuation)
    if sentence_buffer.strip():
        task = asyncio.create_task(
            synthesize_and_send(sentence_buffer.strip(), websocket, kokoro_client)
        )
        tts_tasks.append(task)
    
    # Wait for all TTS tasks to complete
    await asyncio.gather(*tts_tasks)

async def synthesize_and_send(text: str, websocket: WebSocket, kokoro_client):
    """Synthesize one sentence and stream audio chunks to client."""
    async for audio_chunk in kokoro_client.synthesize_stream(text):
        await websocket.send_bytes(audio_chunk)
\end{lstlisting}

\hypertarget{system-prompt-design-for-interview-coach}{%
\subsubsection{System Prompt Design for Interview
Coach}\label{system-prompt-design-for-interview-coach}}

The system prompt is the most important piece of prompt engineering. For
a voice AI interview coach:

\begin{lstlisting}[language=Python]
BEHAVIORAL_INTERVIEWER_SYSTEM_PROMPT = """
You are Alex, a senior engineering manager conducting a behavioral interview. 
Your job is to assess candidates with the rigor of a real interview.

VOICE RULES (critical for audio):
- Keep ALL responses under 40 words unless asking a follow-up question
- NEVER use bullet points, numbers, or markdown — speak in prose
- Use natural conversational fillers: "I see.", "Go on.", "Interesting."
- Speak in complete sentences that sound natural when read aloud
- After the candidate speaks, acknowledge with 1-2 words before your question

INTERVIEW RULES:
- Ask ONE question at a time. Never two questions in one turn.
- Probe incomplete answers. If Situation/Task/Action/Result is missing any component:
  → No Situation: "What was the context? What team or company?"
  → No Result: "What was the actual outcome? Did it ship? What was the impact?"
  → Vague Action: "What did YOU specifically do? What was your decision authority?"
- Push back on clichés: "I'm a team player who..." → "Can you give me a specific example?"
- Challenge weak answers (Challenging/Adversarial mode only):
  "That sounds like what the team did. What would YOU have done differently?"

CANDIDATE CONTEXT:
Name: {candidate_name}
Experience: {years_experience} years
Resume highlights: {resume_summary}
Target role: {target_role}
Target company: {target_company}

INTERVIEW STATE:
Questions asked: {questions_asked}
Current question type: {current_question_type}
Remaining time: {remaining_minutes} minutes

Start by asking your first behavioral question. Choose based on the candidate's experience.
"""
\end{lstlisting}

\hypertarget{context-window-management}{%
\subsubsection{Context Window
Management}\label{context-window-management}}

Each Groq API call costs tokens. Keep context tight:

\begin{lstlisting}[language=Python]
class ConversationContext:
    MAX_TURNS_IN_WINDOW = 6  # Keep last 6 turns verbatim
    MAX_SYSTEM_TOKENS = 800
    MAX_HISTORY_TOKENS = 1000
    
    def build_messages(self, session: Session, new_user_message: str) -> list:
        messages = []
        
        # 1. System prompt (always first)
        messages.append({
            "role": "system",
            "content": self.build_system_prompt(session)
        })
        
        # 2. Last N turns of conversation
        recent_turns = session.turns[-self.MAX_TURNS_IN_WINDOW:]
        for turn in recent_turns:
            messages.append({"role": "user", "content": turn.user_transcript})
            messages.append({"role": "assistant", "content": turn.ai_response})
        
        # 3. Current user message
        messages.append({"role": "user", "content": new_user_message})
        
        return messages
\end{lstlisting}

\hypertarget{multi-provider-fallback-with-circuit-breaker}{%
\subsubsection{Multi-Provider Fallback with Circuit
Breaker}\label{multi-provider-fallback-with-circuit-breaker}}

\begin{lstlisting}[language=Python]
import asyncio
from enum import Enum
from dataclasses import dataclass, field
from datetime import datetime, timedelta

class CircuitState(Enum):
    CLOSED = "closed"     # Normal — requests pass through
    OPEN = "open"         # Failing — requests blocked, use fallback
    HALF_OPEN = "half_open"  # Testing — one request allowed

@dataclass
class CircuitBreaker:
    failure_threshold: int = 5       # Open after 5 failures
    recovery_timeout: int = 60       # Wait 60s before testing
    failure_count: int = 0
    state: CircuitState = CircuitState.CLOSED
    last_failure_time: Optional[datetime] = None
    
    def call_succeeded(self):
        self.failure_count = 0
        self.state = CircuitState.CLOSED
    
    def call_failed(self):
        self.failure_count += 1
        self.last_failure_time = datetime.now()
        if self.failure_count >= self.failure_threshold:
            self.state = CircuitState.OPEN
    
    def can_attempt(self) -> bool:
        if self.state == CircuitState.CLOSED:
            return True
        if self.state == CircuitState.OPEN:
            if datetime.now() - self.last_failure_time > timedelta(seconds=self.recovery_timeout):
                self.state = CircuitState.HALF_OPEN
                return True
            return False
        return True  # HALF_OPEN allows one attempt

# Provider chain with circuit breakers
providers = [
    {"name": "groq", "client": groq_client, "breaker": CircuitBreaker()},
    {"name": "cerebras", "client": cerebras_client, "breaker": CircuitBreaker()},
    {"name": "gemini", "client": gemini_client, "breaker": CircuitBreaker()},
]

async def generate_with_fallback(messages: list) -> str:
    for provider in providers:
        if not provider["breaker"].can_attempt():
            continue
        
        try:
            response = await provider["client"].generate(messages)
            provider["breaker"].call_succeeded()
            return response
        except (RateLimitError, APIError) as e:
            provider["breaker"].call_failed()
            continue
    
    raise Exception("All LLM providers exhausted or circuit-broken")
\end{lstlisting}

\begin{quote}
\textbf{📚 Learn more:} Groq API docs, OpenAI streaming docs,
``Designing Resilient Systems'' (Netflix blog), Circuit Breaker pattern
by Martin Fowler
\end{quote}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{tts-how-kokoro-works}{%
\subsection{8. TTS: How Kokoro Works}\label{tts-how-kokoro-works}}

\hypertarget{neural-tts-pipeline-general}{%
\subsubsection{Neural TTS Pipeline
(General)}\label{neural-tts-pipeline-general}}

Text → Speech is a 3-stage pipeline:

\textbf{Stage 1: Text Normalization} ``Dr.~Smith spent \$3.5M on AI'' →
``Doctor Smith spent three point five million dollars on AI'' Handles
numbers, abbreviations, special characters, URLs.

\textbf{Stage 2: Grapheme-to-Phoneme (G2P)} ``AI'' → /eɪ ˈaɪ/ Converts
text characters to phoneme sequences --- the actual sounds. This is
harder than it looks because English spelling is inconsistent
(``through'', ``tough'', ``though'' --- same ``ough'' but different
sounds).

\textbf{Stage 3: Acoustic Model + Vocoder} Phonemes → mel spectrogram →
waveform

\begin{itemize}
\tightlist
\item
  Acoustic model: maps phonemes to mel spectrogram (what the
  frequency-time representation looks like)
\item
  Vocoder: converts mel spectrogram to actual audio waveform (WaveNet →
  WaveGlow → HiFi-GAN → BigVGAN)
\end{itemize}

\hypertarget{kokoro-specifically}{%
\subsubsection{Kokoro Specifically}\label{kokoro-specifically}}

Kokoro uses \textbf{StyleTTS 2 architecture with ISTFTNet vocoder}:

\begin{itemize}
\tightlist
\item
  Only 82M parameters (vs 300M+ for comparable quality models)
\item
  Uses only the decoder path --- no diffusion model overhead
\item
  ISTFTNet vocoder: converts frequency domain directly to time domain
  via inverse STFT --- much faster than autoregressive vocoders
\item
  \textbf{Real-time factor on CPU: 3--11x} (generates 3--11 seconds of
  audio for each second of compute)
\item
  \textbf{Output: 24 kHz mono audio}
\end{itemize}

\begin{lstlisting}[language=Python]
# Deploy Kokoro with the Kokoro-FastAPI Docker image
# It exposes an OpenAI-compatible TTS endpoint

import httpx
import asyncio

async def synthesize_speech(text: str, voice: str = "af_heart") -> bytes:
    """
    Call local Kokoro TTS API.
    Returns raw audio bytes (PCM or WAV depending on config).
    """
    async with httpx.AsyncClient() as client:
        response = await client.post(
            "http://kokoro:8880/v1/audio/speech",
            json={
                "model": "kokoro",
                "input": text,
                "voice": voice,
                "response_format": "wav",
                "speed": 1.0
            },
            timeout=30.0
        )
        return response.content

# For streaming (returns audio as it generates):
async def synthesize_streaming(text: str) -> AsyncIterator[bytes]:
    async with httpx.AsyncClient() as client:
        async with client.stream(
            "POST",
            "http://kokoro:8880/v1/audio/speech",
            json={"model": "kokoro", "input": text, "voice": "af_heart", 
                  "response_format": "pcm"},
        ) as response:
            async for chunk in response.aiter_bytes(chunk_size=4096):
                yield chunk
\end{lstlisting}

\textbf{Available Kokoro voices:} - \passthrough{\lstinline!af\_heart!}
--- American female, warm - \passthrough{\lstinline!am\_adam!} ---
American male, conversational - \passthrough{\lstinline!bf\_emma!} ---
British female, professional - \passthrough{\lstinline!bm\_george!} ---
British male, authoritative - And 50 more across 8 languages

\begin{quote}
\textbf{📚 Learn more:} hexgrad/kokoro on HuggingFace, StyleTTS 2 paper,
HiFi-GAN paper, Kokoro-FastAPI GitHub
\end{quote}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{full-pipeline-data-flow}{%
\subsection{9. Full Pipeline Data Flow}\label{full-pipeline-data-flow}}

\hypertarget{one-complete-voice-turn-annotated}{%
\subsubsection{One Complete Voice Turn
(Annotated)}\label{one-complete-voice-turn-annotated}}

This is the journey of a single question-answer exchange, with exact
timing targets and failure points.

\begin{lstlisting}
T+0ms: User presses push-to-talk button
       → Client starts MediaRecorder or Web Audio API capture
       → Audio captured at 16kHz, 16-bit, mono

T+20ms: First 20ms audio frame (640 bytes) captured
        → Silero VAD check: probability 0.03 (silence) → buffer but don't trigger
        
T+200ms: User starts speaking "I led the migration..."
         → Silero VAD: probability 0.89 → speech detected
         → Begin collecting frames into speech_buffer
         
T+3800ms: User finishes speaking
           → 500ms of silence detected
           → speech_buffer contains 3.6 seconds of audio (~115 KB PCM)

T+3800ms: ← END OF USER SPEECH | PIPELINE STARTS →

T+3810ms: Audio buffer sent to Deepgram streaming ASR via WebSocket
          [latency target: network RTT ~20ms]

T+4100ms: Deepgram returns partial transcript: "I led the migration of our"
           → Send to client: {"type": "transcript", "text": "...", "is_final": false}
           [Deepgram partial latency: ~300ms from audio end]

T+4250ms: Deepgram returns final transcript: "I led the migration of our monolith to 
           microservices at ECS Tech, saving the company six months of delivery time."
           {"type": "transcript", "text": "...", "is_final": true}
           
T+4260ms: LLM request sent to Groq
           Messages include: system prompt + last 6 turns + this transcript
           ~1,800 tokens total input
           
T+4540ms: First Groq token arrives: "That"
           [Time-to-first-token: ~280ms — within target]
           
T+4600ms: Sentence buffer accumulates: "That's impressive."
           Sentence complete → Send to Kokoro TTS immediately
           
T+4600ms: Kokoro begins synthesizing "That's impressive."
           
T+4680ms: First TTS audio chunk arrives (80ms for 2-word sentence)
           → Send to client: binary WebSocket frame with Opus audio
           
T+4700ms: Client begins playing "That's impressive."
           [T+4700ms - T+3800ms = 900ms total latency — under target!]

T+4540–5200ms: Groq continues generating next sentence
               "You mentioned microservices — what specific challenges did you encounter
               during the migration that you personally had to solve?"
               
T+5100ms: Second sentence complete in LLM stream
           → Kokoro synthesizes while first sentence audio is still playing
           → Client receives and queues second audio chunk

T+5800ms: LLM stream complete (full response)
           "Done generating"

T+6200ms: All TTS audio delivered to client
           → Client finishes playing all audio

T+6210ms: {"type": "turn_complete", "latencies": {
             "asr_ms": 450,
             "llm_ttft_ms": 280,
             "tts_first_ms": 80,
             "total_ms": 900
           }}

T+6210ms: Background task starts:
           → Full turn saved to PostgreSQL (transcript, response, latencies)
           → Score computed by LLM (async, doesn't block next turn)
           → Live scores computed (filler words, WPM from Deepgram output)
           → Valkey session state updated
\end{lstlisting}

\textbf{Total perceived latency: \textasciitilde900ms} (from end of user
speech to first word of AI response)

\hypertarget{where-latency-goes-wrong-and-how-to-fix-it}{%
\subsubsection{Where Latency Goes Wrong (and How to Fix
It)}\label{where-latency-goes-wrong-and-how-to-fix-it}}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Bottleneck
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
How to Detect
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Fix
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
VAD silent threshold too long & asr\_ms \textgreater{} 800ms in logs &
Reduce silence threshold to 350ms \\
Deepgram taking \textgreater500ms & Log Deepgram-specific latency &
Switch to Faster-Whisper locally for this session \\
Groq TTFT \textgreater{} 400ms & llm\_ttft\_ms in logs & Provider in
high-load period → route to Cerebras \\
Kokoro TTS \textgreater{} 200ms per sentence & tts\_first\_ms in logs &
Sentence too long (\textgreater15 words) → add mid-sentence split \\
Network RTT \textgreater{} 100ms & Client-side timestamp comparison &
User far from Oracle region → consider CDN or regional node \\
\end{longtable}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{database-design}{%
\subsection{10. Database Design}\label{database-design}}

\hypertarget{schema-full-production-grade}{%
\subsubsection{Schema (Full,
Production-Grade)}\label{schema-full-production-grade}}

\begin{lstlisting}[language=SQL]
-- Enable UUID generation
CREATE EXTENSION IF NOT EXISTS "pgcrypto";
CREATE EXTENSION IF NOT EXISTS "pg_trgm";  -- For fuzzy text search

-- ─── USERS ───────────────────────────────────────────────────────
CREATE TABLE users (
    id              UUID PRIMARY KEY DEFAULT gen_random_uuid(),
    email           TEXT UNIQUE NOT NULL,
    display_name    TEXT,
    plan            TEXT NOT NULL DEFAULT 'free'  -- 'free', 'pro', 'admin'
                    CHECK (plan IN ('free', 'pro', 'admin')),
    sessions_this_week INTEGER NOT NULL DEFAULT 0,
    week_reset_at   TIMESTAMPTZ,
    created_at      TIMESTAMPTZ NOT NULL DEFAULT NOW(),
    last_seen_at    TIMESTAMPTZ,
    preferences     JSONB NOT NULL DEFAULT '{}'::jsonb
    -- preferences: {"default_voice": "af_heart", "difficulty": "intermediate", ...}
);

-- ─── RESUMES ─────────────────────────────────────────────────────
CREATE TABLE resumes (
    id              UUID PRIMARY KEY DEFAULT gen_random_uuid(),
    user_id         UUID NOT NULL REFERENCES users(id) ON DELETE CASCADE,
    filename        TEXT NOT NULL,
    raw_text        TEXT,           -- Extracted PDF text
    parsed_content  JSONB,          -- Structured: {experience, education, skills, projects}
    target_role     TEXT,
    target_company  TEXT,
    experience_years INTEGER,
    skill_level     TEXT CHECK (skill_level IN ('junior', 'mid', 'senior', 'staff')),
    created_at      TIMESTAMPTZ NOT NULL DEFAULT NOW(),
    is_active       BOOLEAN NOT NULL DEFAULT true
);

-- ─── SESSIONS ────────────────────────────────────────────────────
CREATE TABLE sessions (
    id              UUID PRIMARY KEY DEFAULT gen_random_uuid(),
    user_id         UUID NOT NULL REFERENCES users(id) ON DELETE CASCADE,
    resume_id       UUID REFERENCES resumes(id),
    
    -- Session configuration
    interview_type  TEXT NOT NULL CHECK (interview_type IN 
                    ('behavioral', 'technical', 'system_design', 'mixed')),
    difficulty      TEXT NOT NULL CHECK (difficulty IN 
                    ('beginner', 'intermediate', 'advanced')),
    persona         TEXT NOT NULL CHECK (persona IN 
                    ('friendly', 'neutral', 'challenging', 'adversarial')),
    planned_duration_minutes INTEGER NOT NULL DEFAULT 30,
    
    -- Session state
    status          TEXT NOT NULL DEFAULT 'active' 
                    CHECK (status IN ('active', 'completed', 'abandoned')),
    turn_count      INTEGER NOT NULL DEFAULT 0,
    
    -- Scores (computed after session)
    overall_score   NUMERIC(4,1),    -- 0.0 to 100.0
    content_score   NUMERIC(4,1),
    communication_score NUMERIC(4,1),
    star_score      NUMERIC(4,1),
    confidence_score NUMERIC(4,1),
    filler_score    NUMERIC(4,1),
    
    -- Aggregate stats
    total_words_spoken INTEGER DEFAULT 0,
    avg_wpm         NUMERIC(5,1),
    total_filler_words INTEGER DEFAULT 0,
    avg_response_time_ms INTEGER,
    avg_total_latency_ms INTEGER,
    
    started_at      TIMESTAMPTZ NOT NULL DEFAULT NOW(),
    ended_at        TIMESTAMPTZ,
    
    -- AI-generated summary
    post_session_summary TEXT,
    top_strengths   TEXT[],
    top_improvements TEXT[]
);

-- ─── TURNS ───────────────────────────────────────────────────────
CREATE TABLE turns (
    id              UUID PRIMARY KEY DEFAULT gen_random_uuid(),
    session_id      UUID NOT NULL REFERENCES sessions(id) ON DELETE CASCADE,
    sequence        INTEGER NOT NULL,  -- Order within session
    
    -- Content
    user_transcript TEXT NOT NULL,
    ai_response     TEXT NOT NULL,
    question_type   TEXT,  -- 'behavioral', 'follow_up', 'clarification', 'transition'
    
    -- Scoring
    content_score   NUMERIC(3,1),    -- 1.0 to 5.0
    communication_score NUMERIC(3,1),
    star_score      NUMERIC(3,1),
    confidence_score NUMERIC(3,1),
    filler_score    NUMERIC(3,1),
    overall_score   NUMERIC(3,1),
    
    -- AI feedback (JSONB for flexibility)
    feedback        JSONB,
    -- {
    --   "strengths": ["Clear situation context", "Specific action description"],
    --   "improvements": ["Result was vague — no quantified impact"],
    --   "example_better_answer": "...",
    --   "star_analysis": {"situation": true, "task": true, "action": true, "result": false}
    -- }
    
    -- Speech analytics
    word_count      INTEGER,
    wpm             NUMERIC(5,1),
    filler_count    INTEGER,
    filler_rate_per_min NUMERIC(4,1),
    response_duration_ms INTEGER,  -- How long user spoke
    
    -- Latency breakdown (milliseconds)
    vad_latency_ms  INTEGER,
    asr_latency_ms  INTEGER,
    llm_ttft_ms     INTEGER,
    tts_first_ms    INTEGER,
    total_latency_ms INTEGER,
    
    -- Model tracking (for debugging + A/B testing)
    asr_model       TEXT,  -- 'deepgram-nova-3', 'whisper-small'
    llm_model       TEXT,  -- 'llama-3.3-70b', 'llama-3.1-8b'
    tts_voice       TEXT,  -- 'af_heart'
    llm_provider    TEXT,  -- 'groq', 'cerebras'
    
    -- Storage
    audio_url       TEXT,   -- S3/R2 URL if audio stored
    
    created_at      TIMESTAMPTZ NOT NULL DEFAULT NOW(),
    
    UNIQUE(session_id, sequence)
);

-- ─── QUESTION BANK ───────────────────────────────────────────────
CREATE TABLE questions (
    id              UUID PRIMARY KEY DEFAULT gen_random_uuid(),
    
    -- Content
    text            TEXT NOT NULL,
    category        TEXT NOT NULL CHECK (category IN 
                    ('behavioral', 'technical', 'system_design', 'situational')),
    subcategory     TEXT,  -- 'leadership', 'conflict', 'failure', 'algorithms', etc.
    
    -- Metadata
    difficulty      INTEGER NOT NULL CHECK (difficulty BETWEEN 1 AND 5),
    elo_rating      NUMERIC(6,1) NOT NULL DEFAULT 1200.0,  -- For adaptive difficulty
    
    -- Targeting
    tags            TEXT[] NOT NULL DEFAULT '{}',  -- ['leadership', 'faang', 'senior']
    companies       TEXT[] DEFAULT '{}',           -- ['google', 'amazon', 'meta']
    roles           TEXT[] DEFAULT '{}',           -- ['swe', 'pm', 'ds']
    min_experience_years INTEGER DEFAULT 0,
    
    -- Stats (updated by trigger)
    times_asked     INTEGER NOT NULL DEFAULT 0,
    avg_score       NUMERIC(3,1),
    
    -- Source and quality
    source          TEXT DEFAULT 'curated',  -- 'curated', 'user_contributed'
    is_active       BOOLEAN NOT NULL DEFAULT true,
    
    created_at      TIMESTAMPTZ NOT NULL DEFAULT NOW()
);

-- ─── USER QUESTION HISTORY ───────────────────────────────────────
CREATE TABLE user_question_history (
    id              UUID PRIMARY KEY DEFAULT gen_random_uuid(),
    user_id         UUID NOT NULL REFERENCES users(id) ON DELETE CASCADE,
    question_id     UUID NOT NULL REFERENCES questions(id),
    turn_id         UUID REFERENCES turns(id),
    score           NUMERIC(3,1),
    asked_at        TIMESTAMPTZ NOT NULL DEFAULT NOW(),
    
    -- ELO update tracking
    user_elo_before NUMERIC(6,1),
    user_elo_after  NUMERIC(6,1),
    question_elo_before NUMERIC(6,1),
    question_elo_after NUMERIC(6,1)
);

-- ─── USER ELO RATINGS ────────────────────────────────────────────
CREATE TABLE user_elo_ratings (
    user_id         UUID PRIMARY KEY REFERENCES users(id) ON DELETE CASCADE,
    overall_elo     NUMERIC(6,1) NOT NULL DEFAULT 1200.0,
    behavioral_elo  NUMERIC(6,1) NOT NULL DEFAULT 1200.0,
    technical_elo   NUMERIC(6,1) NOT NULL DEFAULT 1200.0,
    system_design_elo NUMERIC(6,1) NOT NULL DEFAULT 1200.0,
    updated_at      TIMESTAMPTZ NOT NULL DEFAULT NOW()
);

-- ─── INDEXES ──────────────────────────────────────────────────────
-- User lookups
CREATE INDEX idx_users_email ON users(email);

-- Session queries (user dashboard)
CREATE INDEX idx_sessions_user_id_created ON sessions(user_id, started_at DESC);
CREATE INDEX idx_sessions_status ON sessions(status) WHERE status = 'active';

-- Turn queries (session transcript view)
CREATE INDEX idx_turns_session_id_seq ON turns(session_id, sequence);

-- Question bank queries
CREATE INDEX idx_questions_category_difficulty ON questions(category, difficulty);
CREATE INDEX idx_questions_tags ON questions USING GIN(tags);
CREATE INDEX idx_questions_companies ON questions USING GIN(companies);
CREATE INDEX idx_questions_elo ON questions(elo_rating, is_active) WHERE is_active = true;

-- User question history (avoid repeating questions)
CREATE INDEX idx_uqh_user_question ON user_question_history(user_id, question_id);
CREATE INDEX idx_uqh_user_recent ON user_question_history(user_id, asked_at DESC);

-- Latency analytics
CREATE INDEX idx_turns_latency ON turns(total_latency_ms, created_at DESC);
CREATE INDEX idx_turns_llm_provider ON turns(llm_provider, created_at DESC);
\end{lstlisting}

\hypertarget{common-query-patterns}{%
\subsubsection{Common Query Patterns}\label{common-query-patterns}}

\begin{lstlisting}[language=SQL]
-- User's recent sessions with scores
SELECT s.id, s.interview_type, s.difficulty, s.overall_score, 
       s.turn_count, s.started_at, s.ended_at
FROM sessions s
WHERE s.user_id = $1
  AND s.status = 'completed'
ORDER BY s.started_at DESC
LIMIT 20;

-- Score trend for dashboard chart (last 30 sessions)
SELECT 
    s.started_at::date as date,
    AVG(s.overall_score) as avg_score,
    AVG(s.content_score) as avg_content,
    AVG(s.communication_score) as avg_comm,
    AVG(s.star_score) as avg_star
FROM sessions s
WHERE s.user_id = $1
  AND s.status = 'completed'
  AND s.started_at > NOW() - INTERVAL '60 days'
GROUP BY date
ORDER BY date;

-- Find questions user hasn't seen in this category
SELECT q.id, q.text, q.difficulty, q.elo_rating
FROM questions q
WHERE q.category = $1
  AND q.is_active = true
  AND q.id NOT IN (
      SELECT uqh.question_id 
      FROM user_question_history uqh
      WHERE uqh.user_id = $2
        AND uqh.asked_at > NOW() - INTERVAL '7 days'
  )
ORDER BY ABS(q.elo_rating - $3)  -- Closest to user's ELO
LIMIT 10;

-- Latency percentiles for monitoring
SELECT 
    percentile_cont(0.50) WITHIN GROUP (ORDER BY total_latency_ms) as p50,
    percentile_cont(0.95) WITHIN GROUP (ORDER BY total_latency_ms) as p95,
    percentile_cont(0.99) WITHIN GROUP (ORDER BY total_latency_ms) as p99
FROM turns
WHERE created_at > NOW() - INTERVAL '24 hours';
\end{lstlisting}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{caching-layer-valkey}{%
\subsection{11. Caching Layer: Valkey}\label{caching-layer-valkey}}

\hypertarget{what-valkey-is-and-why-we-use-it}{%
\subsubsection{What Valkey Is and Why We Use
It}\label{what-valkey-is-and-why-we-use-it}}

Valkey is a Redis-compatible in-memory data store. It keeps data in RAM
--- reads and writes complete in \textbf{\textless1ms} (vs 5--20ms for
PostgreSQL). It's the right tool for ephemeral session data that needs
to be fast.

\textbf{Valkey data structures we use:}

\begin{lstlisting}[language=Python]
import valkey.asyncio as valkey

redis = valkey.from_url("redis://valkey:6379", decode_responses=False)

# 1. SESSION STATE (Hash) — Active session data
# Key: session:{session_id}
# TTL: 2 hours (auto-expire if user disconnects)
await redis.hset(f"session:{session_id}", mapping={
    "user_id": user_id,
    "interview_type": "behavioral",
    "turn_count": "0",
    "last_active": str(time.time())
})
await redis.expire(f"session:{session_id}", 7200)  # 2-hour TTL

# 2. LLM CONTEXT CACHE (String + JSON) — Recent conversation history
# Key: context:{session_id}  
# TTL: 1 hour (expire if idle)
context = {"messages": messages_list, "turn_count": 5}
await redis.set(
    f"context:{session_id}", 
    json.dumps(context), 
    ex=3600  # 1-hour TTL
)
context_str = await redis.get(f"context:{session_id}")

# 3. RATE LIMITING (String + INCR) — Sliding window counter
# Key: ratelimit:{user_id}:{window}
async def check_rate_limit(user_id: str, limit: int = 100) -> bool:
    window = int(time.time() // 3600)  # 1-hour windows
    key = f"ratelimit:{user_id}:{window}"
    
    count = await redis.incr(key)
    if count == 1:
        await redis.expire(key, 3600)  # Expire at end of window
    
    return count <= limit

# 4. JWT REVOCATION (Set with TTL)
# Key: revoked_tokens:{user_id}
await redis.sadd(f"revoked_tokens:{user_id}", token_jti)
await redis.expire(f"revoked_tokens:{user_id}", 86400)  # 24 hours

# 5. WEBSOCKET CONNECTION MAP (Hash)
# Useful when running multiple server instances
# Key: ws_connections
await redis.hset("ws_connections", session_id, server_instance_id)

# 6. DAILY SESSION COUNT (String)
# Key: sessions:{user_id}:{date}
date_str = datetime.now().strftime("%Y-%m-%d")
count = await redis.incr(f"sessions:{user_id}:{date_str}")
await redis.expire(f"sessions:{user_id}:{date_str}", 86400)
\end{lstlisting}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{authentication-security}{%
\subsection{12. Authentication +
Security}\label{authentication-security}}

\hypertarget{jwt-authentication-flow}{%
\subsubsection{JWT Authentication Flow}\label{jwt-authentication-flow}}

\begin{lstlisting}[language=Python]
from datetime import datetime, timedelta
from jose import JWTError, jwt
from passlib.context import CryptContext
from fastapi import Depends, HTTPException, Cookie
from fastapi.security import HTTPBearer, HTTPAuthorizationCredentials

SECRET_KEY = os.environ["JWT_SECRET_KEY"]  # 32+ byte random string
ALGORITHM = "HS256"
ACCESS_TOKEN_EXPIRE_MINUTES = 15
REFRESH_TOKEN_EXPIRE_DAYS = 7

pwd_context = CryptContext(schemes=["bcrypt"], deprecated="auto")
bearer = HTTPBearer()

def create_access_token(user_id: str) -> str:
    payload = {
        "sub": user_id,
        "exp": datetime.utcnow() + timedelta(minutes=ACCESS_TOKEN_EXPIRE_MINUTES),
        "type": "access",
        "jti": str(uuid.uuid4())  # Unique token ID for revocation
    }
    return jwt.encode(payload, SECRET_KEY, algorithm=ALGORITHM)

def create_refresh_token(user_id: str) -> str:
    payload = {
        "sub": user_id,
        "exp": datetime.utcnow() + timedelta(days=REFRESH_TOKEN_EXPIRE_DAYS),
        "type": "refresh",
        "jti": str(uuid.uuid4())
    }
    return jwt.encode(payload, SECRET_KEY, algorithm=ALGORITHM)

# Login endpoint
@app.post("/api/auth/login")
async def login(credentials: LoginRequest, response: Response):
    user = await verify_user(credentials.email, credentials.password)
    
    access_token = create_access_token(str(user.id))
    refresh_token = create_refresh_token(str(user.id))
    
    # Store refresh token in httpOnly cookie (not accessible by JS)
    response.set_cookie(
        key="refresh_token",
        value=refresh_token,
        httponly=True,   # JS cannot read this
        secure=True,     # HTTPS only
        samesite="strict",  # CSRF protection
        max_age=7 * 24 * 3600  # 7 days
    )
    
    # Return access token in response body (stored in memory, not localStorage)
    return {"access_token": access_token, "token_type": "bearer"}

# Dependency for protected routes
async def get_current_user(
    credentials: HTTPAuthorizationCredentials = Depends(bearer)
) -> User:
    try:
        payload = jwt.decode(credentials.credentials, SECRET_KEY, algorithms=[ALGORITHM])
        user_id = payload.get("sub")
        token_jti = payload.get("jti")
        
        # Check revocation list
        is_revoked = await redis.sismember(f"revoked_tokens:{user_id}", token_jti)
        if is_revoked:
            raise HTTPException(status_code=401, detail="Token revoked")
        
        return await get_user_by_id(user_id)
    except JWTError:
        raise HTTPException(status_code=401, detail="Invalid token")
\end{lstlisting}

\hypertarget{rate-limiting-middleware}{%
\subsubsection{Rate Limiting
Middleware}\label{rate-limiting-middleware}}

\begin{lstlisting}[language=Python]
from fastapi import Request
from starlette.middleware.base import BaseHTTPMiddleware

class RateLimitMiddleware(BaseHTTPMiddleware):
    
    LIMITS = {
        "/api/auth/": {"requests": 5, "window_seconds": 60},
        "/api/": {"requests": 60, "window_seconds": 60},
        "/ws/": {"connections": 3, "window_seconds": None},  # Concurrent limit
    }
    
    async def dispatch(self, request: Request, call_next):
        client_ip = request.client.host
        path = request.url.path
        
        # Determine applicable limit
        for prefix, limit in self.LIMITS.items():
            if path.startswith(prefix):
                key = f"rl:{client_ip}:{prefix}"
                
                if limit.get("window_seconds"):
                    count = await redis.incr(key)
                    if count == 1:
                        await redis.expire(key, limit["window_seconds"])
                    
                    if count > limit["requests"]:
                        return JSONResponse(
                            status_code=429,
                            content={"detail": "Rate limit exceeded"},
                            headers={"Retry-After": str(limit["window_seconds"])}
                        )
                break
        
        return await call_next(request)
\end{lstlisting}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{infrastructure-architecture}{%
\subsection{13. Infrastructure
Architecture}\label{infrastructure-architecture}}

\hypertarget{docker-compose-production}{%
\subsubsection{Docker Compose
(Production)}\label{docker-compose-production}}

\begin{lstlisting}
# docker-compose.prod.yml

networks:
  frontend:       # Caddy + FastAPI
    driver: bridge
  backend:        # FastAPI + Valkey + databases (isolated)
    driver: bridge
    internal: true  # Cannot reach internet directly

volumes:
  kokoro_models:  # Pre-downloaded TTS models
  valkey_data:    # Persistent Valkey data

services:
  
  caddy:
    image: caddy:2-alpine
    ports:
      - "80:80"
      - "443:443"
    volumes:
      - ./Caddyfile:/etc/caddy/Caddyfile:ro
      - caddy_data:/data
    networks: [frontend]
    restart: unless-stopped
    deploy:
      resources:
        limits: {memory: 128m}
  
  app:
    build:
      context: .
      dockerfile: Dockerfile
      target: production
    environment:
      - DATABASE_URL=${DATABASE_URL}
      - VALKEY_URL=redis://valkey:6379
      - GROQ_API_KEY=${GROQ_API_KEY}
      - DEEPGRAM_API_KEY=${DEEPGRAM_API_KEY}
      - JWT_SECRET_KEY=${JWT_SECRET_KEY}
      - WHISPER_URL=http://whisper:9000
      - KOKORO_URL=http://kokoro:8880
      - NEW_RELIC_LICENSE_KEY=${NEW_RELIC_LICENSE_KEY}
      - SENTRY_DSN=${SENTRY_DSN}
      - POSTHOG_API_KEY=${POSTHOG_API_KEY}
    networks: [frontend, backend]
    restart: unless-stopped
    depends_on: [valkey, whisper, kokoro]
    deploy:
      resources:
        limits: {memory: 2g}
    healthcheck:
      test: ["CMD", "curl", "-f", "http://localhost:8000/api/health"]
      interval: 30s
      timeout: 10s
      retries: 3
  
  whisper:
    image: fedirz/faster-whisper-server:latest-cpu
    environment:
      - WHISPER__MODEL=small
      - WHISPER__LANGUAGE=en
    networks: [backend]
    restart: unless-stopped
    deploy:
      resources:
        limits: {memory: 1g, cpus: "1.0"}
  
  kokoro:
    image: ghcr.io/remsky/kokoro-fastapi-cpu:latest
    volumes:
      - kokoro_models:/app/models
    networks: [backend]
    restart: unless-stopped
    deploy:
      resources:
        limits: {memory: 2g, cpus: "1.5"}
  
  valkey:
    image: valkey/valkey:8-alpine
    command: >
      valkey-server
      --maxmemory 512mb
      --maxmemory-policy allkeys-lru
      --save 60 100
    volumes:
      - valkey_data:/data
    networks: [backend]
    restart: unless-stopped
    deploy:
      resources:
        limits: {memory: 600m}

volumes:
  caddy_data:
  kokoro_models:
  valkey_data:
\end{lstlisting}

\hypertarget{caddyfile}{%
\subsubsection{Caddyfile}\label{caddyfile}}

\begin{lstlisting}
# Caddyfile — Automatic HTTPS, WebSocket support, API routing

{
    email your@email.com
}

api.speakprep.com {
    # WebSocket connections (long-lived)
    handle /ws/* {
        reverse_proxy app:8000 {
            flush_interval -1  # Critical: disables buffering for WebSockets
            transport http {
                read_timeout 1h   # Allow 1-hour sessions
                write_timeout 1h
            }
        }
    }
    
    # REST API
    handle /api/* {
        reverse_proxy app:8000
    }
    
    # Security headers
    header {
        Strict-Transport-Security "max-age=31536000; includeSubDomains"
        X-Content-Type-Options "nosniff"
        X-Frame-Options "DENY"
        -Server  # Remove Caddy server header
    }
}

# Web app (deployed separately on Cloudflare Pages — redirect here)
speakprep.com {
    redir https://app.speakprep.com{uri}
}
\end{lstlisting}

\hypertarget{cicd-pipeline}{%
\subsubsection{CI/CD Pipeline}\label{cicd-pipeline}}

\begin{lstlisting}
# .github/workflows/deploy.yml
name: Deploy to Production

on:
  push:
    branches: [main]

jobs:
  lint-and-test:
    runs-on: ubuntu-latest
    services:
      postgres:
        image: postgres:16
        env:
          POSTGRES_PASSWORD: test
          POSTGRES_DB: speakprep_test
        options: >-
          --health-cmd pg_isready
          --health-interval 10s
          --health-timeout 5s
          --health-retries 5
      
      valkey:
        image: valkey/valkey:8-alpine
        options: >-
          --health-cmd "valkey-cli ping"
          --health-interval 10s
    
    steps:
      - uses: actions/checkout@v4
      
      - name: Set up Python
        uses: actions/setup-python@v5
        with:
          python-version: '3.12'
          cache: 'pip'
      
      - name: Install dependencies
        run: pip install -r requirements.txt -r requirements-dev.txt
      
      - name: Lint (ruff)
        run: ruff check . && ruff format --check .
      
      - name: Type check (mypy)
        run: mypy app/ --strict
      
      - name: Run tests
        env:
          DATABASE_URL: postgresql://postgres:test@localhost/speakprep_test
          VALKEY_URL: redis://localhost:6379
          JWT_SECRET_KEY: test-secret-key-minimum-32-characters
        run: pytest tests/ -v --cov=app --cov-report=xml
  
  build-and-push:
    needs: lint-and-test
    runs-on: ubuntu-latest
    steps:
      - uses: actions/checkout@v4
      
      - name: Set up Docker Buildx
        uses: docker/setup-buildx-action@v3
      
      - name: Login to GHCR
        uses: docker/login-action@v3
        with:
          registry: ghcr.io
          username: ${{ github.actor }}
          password: ${{ secrets.GITHUB_TOKEN }}
      
      - name: Build and push
        uses: docker/build-push-action@v5
        with:
          context: .
          platforms: linux/arm64   # Oracle ARM
          push: true
          tags: ghcr.io/${{ github.repository }}:latest
          cache-from: type=gha
          cache-to: type=gha,mode=max
  
  deploy:
    needs: build-and-push
    runs-on: ubuntu-latest
    steps:
      - name: Deploy to Oracle ARM
        uses: appleboy/ssh-action@v1
        with:
          host: ${{ secrets.ORACLE_HOST }}
          username: ubuntu
          key: ${{ secrets.ORACLE_SSH_KEY }}
          script: |
            cd ~/speakprep
            git pull origin main
            docker compose -f docker-compose.prod.yml pull
            docker compose -f docker-compose.prod.yml up -d --force-recreate app
            
            # Run migrations
            docker compose -f docker-compose.prod.yml exec -T app \
              alembic upgrade head
            
            # Health check
            sleep 10
            curl -f http://localhost:8000/api/health || exit 1
            
            # Clean up old images
            docker image prune -f
\end{lstlisting}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{observability-monitoring}{%
\subsection{14. Observability +
Monitoring}\label{observability-monitoring}}

\hypertarget{health-check-endpoint}{%
\subsubsection{Health Check Endpoint}\label{health-check-endpoint}}

\begin{lstlisting}[language=Python]
@app.get("/api/health")
async def health_check() -> dict:
    """
    Returns overall system health.
    Load balancers and monitoring systems call this.
    Return 200 if healthy, 503 if degraded/unhealthy.
    """
    health = {
        "status": "healthy",
        "timestamp": datetime.utcnow().isoformat(),
        "version": os.environ.get("APP_VERSION", "unknown"),
        "checks": {}
    }
    
    # Check PostgreSQL
    try:
        await db.execute("SELECT 1")
        health["checks"]["database"] = "healthy"
    except Exception as e:
        health["checks"]["database"] = f"unhealthy: {str(e)}"
        health["status"] = "unhealthy"
    
    # Check Valkey
    try:
        await redis.ping()
        health["checks"]["cache"] = "healthy"
    except Exception as e:
        health["checks"]["cache"] = f"unhealthy: {str(e)}"
        health["status"] = "degraded"  # Can run without cache
    
    # Check Kokoro TTS
    try:
        async with httpx.AsyncClient() as client:
            resp = await client.get("http://kokoro:8880/health", timeout=2.0)
            health["checks"]["tts"] = "healthy" if resp.status_code == 200 else "unhealthy"
    except Exception:
        health["checks"]["tts"] = "unhealthy"
        health["status"] = "degraded"
    
    # Check Whisper ASR  
    try:
        async with httpx.AsyncClient() as client:
            resp = await client.get("http://whisper:9000/health", timeout=2.0)
            health["checks"]["asr"] = "healthy" if resp.status_code == 200 else "unhealthy"
    except Exception:
        health["checks"]["asr"] = "degraded"  # Deepgram is fallback
    
    # Current load
    health["active_sessions"] = len(manager.active_connections)
    
    status_code = 200 if health["status"] == "healthy" else 503
    return JSONResponse(content=health, status_code=status_code)
\end{lstlisting}

\hypertarget{structured-latency-logging}{%
\subsubsection{Structured Latency
Logging}\label{structured-latency-logging}}

\begin{lstlisting}[language=Python]
import structlog

log = structlog.get_logger()

async def process_turn(session, audio_data):
    t_start = time.monotonic()
    
    # ASR
    t_asr_start = time.monotonic()
    transcript = await transcribe(audio_data)
    asr_ms = int((time.monotonic() - t_asr_start) * 1000)
    
    # LLM
    t_llm_start = time.monotonic()
    llm_ttft_ms = None
    
    async def on_first_token():
        nonlocal llm_ttft_ms
        llm_ttft_ms = int((time.monotonic() - t_llm_start) * 1000)
    
    response = await generate_response(transcript, on_first_token_callback=on_first_token)
    llm_total_ms = int((time.monotonic() - t_llm_start) * 1000)
    
    # TTS
    t_tts_start = time.monotonic()
    await synthesize_and_stream(response)
    tts_ms = int((time.monotonic() - t_tts_start) * 1000)
    
    total_ms = int((time.monotonic() - t_start) * 1000)
    
    # Structured log — shipped to New Relic
    log.info(
        "turn_completed",
        session_id=session.id,
        user_id=session.user_id,
        turn_sequence=session.turn_count,
        asr_ms=asr_ms,
        llm_ttft_ms=llm_ttft_ms,
        llm_total_ms=llm_total_ms,
        tts_ms=tts_ms,
        total_ms=total_ms,
        asr_model=ASR_MODEL,
        llm_model=LLM_MODEL,
        llm_provider=LLM_PROVIDER,
    )
    
    # Save to DB
    await save_turn_latencies(session.id, {
        "asr_ms": asr_ms, 
        "llm_ttft_ms": llm_ttft_ms, 
        "tts_first_ms": tts_ms,
        "total_ms": total_ms
    })
    
    # Alert if > 4 seconds
    if total_ms > 4000:
        log.warning("high_latency_turn", total_ms=total_ms, session_id=session.id)
\end{lstlisting}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{architecture-decision-records-adrs}{%
\subsection{15. Architecture Decision Records
(ADRs)}\label{architecture-decision-records-adrs}}

Each ADR is a permanent record. Written before the decision. Never
deleted --- only superseded.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{adr-001-websocket-over-rest-or-grpc}{%
\subsubsection{ADR-001: WebSocket over REST or
gRPC}\label{adr-001-websocket-over-rest-or-grpc}}

\textbf{Date:} April 2026 \textbar{} \textbf{Status:} Accepted
\textbar{} \textbf{Deciders:} Abhiyan Sainju

\textbf{Context:} Real-time voice requires bidirectional communication.
We must choose a protocol.

\textbf{Options:} 1. \textbf{REST long-polling} --- Client polls every
100ms for new data 2. \textbf{Server-Sent Events (SSE)} ---
One-directional push from server to client 3. \textbf{WebSockets} ---
Full-duplex persistent connection 4. \textbf{WebRTC} --- Peer-to-peer
protocol for real-time audio/video 5. \textbf{gRPC streaming} --- Binary
RPC with bidirectional streaming

\textbf{Decision:} WebSockets

\textbf{Rationale:} - REST polling: 100ms artificial latency, 10x
unnecessary requests, no binary data support - SSE: One-directional ---
can't send audio from client to server - WebRTC: Designed for P2P video;
requires complex signaling server; massive overkill - gRPC: Excellent
for service-to-service, but browser support requires grpc-web proxy;
adds complexity without benefit - WebSockets: Bidirectional,
binary-capable, universally supported in browsers and React Native,
2-byte frame overhead vs 700+ bytes for HTTP

\textbf{Consequences:} - Must implement reconnection logic (WebSocket
connections can drop) - Load balancers need sticky sessions for
multi-server deployment - More complex debugging than REST (can't use
curl --- need wscat or browser dev tools) - ✅ Enables real-time
streaming in both directions with minimal overhead

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{adr-002-web-first-no-mobile-in-phase-1}{%
\subsubsection{ADR-002: Web-First (No Mobile in Phase
1)}\label{adr-002-web-first-no-mobile-in-phase-1}}

\textbf{Date:} April 2026 \textbar{} \textbf{Status:} Accepted

\textbf{Context:} Should we build mobile (React Native) in Phase 1
alongside web?

\textbf{Options:} 1. Build web + mobile simultaneously 2. Web-first,
mobile in Phase 2 3. Mobile-first (PWA or native)

\textbf{Decision:} Web-first, mobile in Phase 2

\textbf{Rationale:} - React Native audio APIs
(\passthrough{\lstinline!expo-av!},
\passthrough{\lstinline!expo-audio!}) have documented instability
issues, particularly on iOS for real-time streaming - Mobile builds take
significantly longer per iteration (10-minute EAS build vs instant Vite
dev server) - Browser Web Audio API is mature and gives precise control
over audio capture - Can test and iterate 3--5x faster on web - Most
interview prep happens at a desk (desktop/laptop browser)

\textbf{Consequences:} - Phase 1 users limited to desktop browsers -
Chrome, Firefox, Safari, Edge are primary targets - Mobile is Phase 2
--- architecture must not require rewrite to add it

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{adr-003-groq-as-primary-llm-provider}{%
\subsubsection{ADR-003: Groq as Primary LLM
Provider}\label{adr-003-groq-as-primary-llm-provider}}

\textbf{Date:} April 2026 \textbar{} \textbf{Status:} Accepted

\textbf{Context:} Which LLM provider to use for generating interview
responses?

\textbf{Decision:} Groq (Llama 3.3 70B) as primary, Cerebras as
secondary fallback, Gemini Flash-Lite as tertiary

\textbf{Rationale:} - Groq: Sub-100ms TTFT via LPU hardware. At 315
tokens/sec, a 50-word AI response takes \textasciitilde0.2 seconds to
generate. This is the single most important metric for voice AI. -
OpenAI GPT-4o: 300--800ms TTFT --- too slow for natural conversation
feel - Self-hosted Llama (Ollama): 5--15 tokens/sec on ARM CPU --- far
too slow for real-time voice - Cerebras: 2,500 tokens/sec, 80--150ms
TTFT --- excellent backup. Fewer model options. - Groq free tier: 30
RPM, 500K tokens/day --- sufficient for development and early users

\textbf{Assumptions (must validate):} - Groq free tier remains available
as user base grows - Llama 3.3 70B quality is sufficient for interview
coaching (vs GPT-4o)

\textbf{Consequences:} - Must implement multi-provider fallback for rate
limit handling - Tied to Groq's model availability --- may need to
update model string periodically - OpenAI-compatible API format allows
switching providers with minimal code change

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{adr-004-kokoro-tts-self-hosted-as-primary-tts}{%
\subsubsection{ADR-004: Kokoro TTS (Self-Hosted) as Primary
TTS}\label{adr-004-kokoro-tts-self-hosted-as-primary-tts}}

\textbf{Date:} April 2026 \textbar{} \textbf{Status:} Accepted

\textbf{Context:} Which TTS engine for voice responses?

\textbf{Decision:} Kokoro TTS self-hosted via Kokoro-FastAPI Docker
image

\textbf{Rationale:} - ElevenLabs: 10,000 chars/month free =
\textasciitilde10 minutes of audio. Unsustainable at any scale. -
Cartesia: 20,000 chars/month + \$5/month for usable limits. Good for
later. - Google Cloud TTS: 4M chars/month free, but quality is 6/10 on
Standard voices. - Kokoro: Apache 2.0, 8.5/10 quality (\#1 HuggingFace
TTS Arena), runs on CPU, unlimited usage, 54 voices, \textless300ms
latency per sentence.

\textbf{Consequences:} - Consumes \textasciitilde1--2 GB RAM on Oracle
ARM (within 24 GB budget) - No voice cloning in Phase 1 (fixed voices
only) - Must maintain Docker deployment --- no vendor SLA - \textbf{When
paid users demand higher quality:} Add Cartesia at \$0.002/char as Pro
upgrade

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{adr-005-deepgram-for-streaming-asr-over-faster-whisper-only}{%
\subsubsection{ADR-005: Deepgram for Streaming ASR (over
Faster-Whisper-only)}\label{adr-005-deepgram-for-streaming-asr-over-faster-whisper-only}}

\textbf{Date:} April 2026 \textbar{} \textbf{Status:} Accepted

\textbf{Context:} Use external streaming ASR (Deepgram) or self-hosted
Whisper?

\textbf{Decision:} Deepgram as primary (uses \$200 free credit),
Faster-Whisper as fallback

\textbf{Rationale:} - Faster-Whisper requires batch processing ---
collect full audio, then transcribe. Adds 100--500ms latency vs
Deepgram's native streaming. - Deepgram returns partial transcripts
300ms after speech starts (before user finishes talking). This enables
``transcript-while-speaking'' UI feature. - Deepgram's nova-3 model
achieves \textless5\% WER vs Whisper's 8--10\% on conversational speech.
- \$200 free credit = \textasciitilde26,000 minutes. At 20 minutes/user
× 100 test users = 2,000 minutes. Credit lasts well through Phase 1.

\textbf{Assumptions:} - \$200 credit provides sufficient runway through
Phase 1 launch - Self-hosted Faster-Whisper covers fallback adequately

\textbf{Consequences:} - External API dependency for primary ASR path -
When Deepgram credit exhausted: migrate to self-hosted Faster-Whisper
(already built)

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{adr-006-supabase-for-phase-1-database-auth}{%
\subsubsection{ADR-006: Supabase for Phase 1 Database +
Auth}\label{adr-006-supabase-for-phase-1-database-auth}}

\textbf{Date:} April 2026 \textbar{} \textbf{Status:} Accepted (Phase 1
only, revisit at 500 users)

\textbf{Decision:} Use Supabase free tier for PostgreSQL + Auth

\textbf{Rationale:} - Supabase bundles: PostgreSQL + JWT auth +
Row-Level Security + Storage + real-time - Self-building auth (password
hashing, JWT issuance, token refresh, email verification) takes 2--3
weeks - Supabase saves those weeks for Phase 1 core product work - 500
MB storage is sufficient for text-only session data (no audio storage) -
Pause prevention: automated cron job hitting
\passthrough{\lstinline!/api/health!} every 6 days

\textbf{Consequences:} - 500 MB storage limit --- must migrate to
self-hosted PostgreSQL on Oracle by \textasciitilde500 users - Supabase
as single point of failure --- acceptable for Phase 1 - Row-Level
Security policies should be written from day 1 so migration doesn't
require schema rewrite

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{End of Document 2 --- System Design + Architecture} \emph{Next:
Document 3 --- Phase-by-Phase Build Guide with Learning Curriculum}

\end{document}
